### 2018-05-04 manuscript.rmd
mapped traits to BI topology

Euphysonectae consists of two reciprocally monophyletic groups that we here provisionally refer to as Clade A and Clade B (Fig. 3A). The presence of an involucrum, a fold around the base of the cnidoband [@totton1965synopsis], is a potential synapomorphy for Clade A. Species of Clade A also have a descending mantle canal within the nectophores (Fig. S6), a structure that is also present in some calycophorans. Members of Clade A are also monoecious (Fig. 5). There is not a clear synapomorphy for Clade B. Within Clade B there is low support for the placement of *Erenna richardi*, which is placed as sister to Clade A in some analyses (Fig. 3B). More taxon sampling will be required to determine the relationship of species within this clade.

@@

Within Calycophorae, taxon sampling is less comprehensive here than in the previous study. The calycophoran relationships that can be investigated, however, are in broad agreement with the previous analysis. Calycophorans have in the past been split into two groups, prayomorphs and diphyomorphs, based on morphology after @mackie1987siphonophore. As in the previous study, the results presented here indicate that the prayomorphs are paraphyletic with respect to the diphyomorphs. *Craseoa lathetica* and *Desmophyes* sp. are sister to *Hippopodius hippopus* in this study, while in the previous study, the relationship between *C. lathetica* and the clade including *H. hippopus* was unresolved.

@@

>>>>

In ML analyses Euphysonectae consists of two reciprocally monophyletic groups that we here provisionally refer to as Clade A and Clade B (Fig. 3A). In BI analyses, clade B is graded (Fig. 3B). The presence of an involucrum, a fold around the base of the cnidoband [@totton1965synopsis], is a potential synapomorphy for Clade A. Species of Clade A also have a descending mantle canal within the nectophores (Fig. S6), a structure that is also present in some calycophorans. Members of Clade A are also monoecious (Fig. 5). There is not a clear synapomorphy for Clade B. Within Clade B there is high support for the placement of *Erenna richardi* in ML analyses, but it is placed as sister to Clade A in BI analyses (Fig. 3B). More taxon sampling will be required to determine the relationship of species within this clade.

@@

Within Calycophorae, taxon sampling is less comprehensive here than in the previous study. The calycophoran relationships that can be investigated, however, are in broad agreement with the previous analysis. Calycophorans have in the past been split into two groups, prayomorphs and diphyomorphs, based on morphology after @mackie1987siphonophore. As in the previous study, the results presented here indicate that the prayomorphs are paraphyletic with respect to the diphyomorphs. In the previous study, the relationship between *C. lathetica* and the clade including *H. hippopus* was unresolved. In this study, *Craseoa lathetica* and *Desmophyes* sp. are sister to *Hippopodius hippopus* in ML analyses with high support, while in BI analyses, *H. hippopus* is sister to *Lilyopsis fluoracantha* and the diphyomorphs (Fig. 3B).

@@

```{r BI tree ancestral trait reconstructions}

BIspeciestree<-read.tree(file="agalma/Outfiles/combined_trimmed60_poisson.con.tre")
BIspeciestree = ape::ladderize( BIspeciestree )

BIspeciestree = fix_names( BIspeciestree )

BIspeciestree =
	  ape::root(
	    BIspeciestree,
	    c( "Nematostella vectensis", "Aiptasia pallida" ),
	    resolve.root=TRUE
	   )

tree<-BIspeciestree

tree <- drop.tip(tree, which(!(tree$tip.label %in% rownames(cdata))))

ultratree <- chronos(tree)
class( ultratree  ) = "phylo"

dpruned_tree <- drop.tip(ultratree, which(!(ultratree$tip.label %in% rownames(dpruned_data))))
dpruned_data <- dpruned_data[match(dpruned_tree$tip.label, rownames(dpruned_data)),]

depth_median = dpruned_data$Depth.Median
names(depth_median) = rownames(dpruned_data)

#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree , sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree , palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree , tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree , tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree , nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree , bracts, nsim = 100, message=FALSE) -> bracts_sim
#print("SIMMAP Habitat")

#Nectophore position SIMMAP setup
NectoPosTree = drop.tip(ultratree , which(!(ultratree $tip.label %in% names(necto_pos))))
make.simmap(NectoPosTree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim

#Descending mantle Canal SIMMAP Setup
DescMantleTree =  drop.tip(ultratree , which(!(ultratree $tip.label %in% names(desc_mantle))))
make.simmap(DescMantleTree, desc_mantle, nsim = 100, message=FALSE) -> desc_mantle_sim
```

```{r BI mono, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of sexual characters on the consensus Bayesian tree topology." }
#Simmap SEX
sex_obj <- densityMap(sex_sim, plot=FALSE)
sex_obj$cols[1:length(sex_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(sex_obj$cols))
 plot(sex_obj)
```

```{r BI palp, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of palpon presence/absence on the consensus Bayesian tree topology." }
#Simmap PALPONS
palpons_obj <- densityMap(palpons_sim, plot=FALSE)
palpons_obj$cols[1:length(palpons_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(palpons_obj$cols))

plot(palpons_obj)
```

```{r tentilla BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as not bearing tentilla, mapped on the consensus Bayesian tree topology."}
tentilla_obj <- densityMap(tentilla_sim,plot=FALSE)
tentilla_obj$cols[1:length(tentilla_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla_obj$cols))
plot(tentilla_obj)
```

```{r tentilla ext BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as bearing tentilla, mapped on the consensus Bayesian tree topology."}
tentilla2_obj <- densityMap(tentilla_sim2, plot=FALSE)
tentilla2_obj$cols[1:length(tentilla2_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla2_obj$cols))
plot(tentilla2_obj)
```

```{r nectosome BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome, mapped on the consensus Bayesian tree topology."}
nectosome_obj <- densityMap(nectosome_sim, plot=FALSE)
nectosome_obj$cols[1:length(nectosome_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(nectosome_obj$cols))
plot(nectosome_obj)
```

```{r mantle BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of a descending mantle canal in the nectophores, mapped on the consensus Bayesian tree topology."}
desc_mantle_obj <- densityMap(desc_mantle_sim, plot=FALSE)
desc_mantle_obj$cols[1:length(desc_mantle_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(desc_mantle_obj$cols))
plot(desc_mantle_obj)
```

```{r necto BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map for the evolution of the position of the nectosome, mapped on the consensus Bayesian tree topology."}
necto_pos_obj <- densityMap(necto_pos_sim, plot=FALSE)
necto_pos_obj$cols[1:length(necto_pos_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(necto_pos_obj$cols))
plot(necto_pos_obj)
```

```{r depth BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species observed with an MBARI ROV, mapped on the consensus Bayesian tree topology."}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

```{r depth BI extended, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations, mapped on the consensus Bayesian tree topology."}
median_extended = cdata$Depth.Median.Extended
names(median_extended) = rownames(cdata)
median_extended = median_extended[match(names(median_extended), ultratree$tip.label)]
depthmap_ext <- contMap(ultratree, median_extended, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap_ext)
